Finding shortest and closest vectors in a lattice of Voronoi's first kind

### 2014-04-22 talk/presentation.tex
added to talk

\title{Finding shortest and closest vectors in a lattice of Voronoi's first kind}
\author{Robby McKilliam \\
\vspace{0.2cm}
Alex Grant \\ Vaughan Clarkson \\
\vspace{0.7cm}
{\small
Institute for Telecommunications Research \\ University of South Australia 
\\ \vspace{0.2cm}
School of Information Technology and Electrical Engineering \\ The University of Queensland
}
}

@@

\frame{
\frametitle{A series of relevant vectors}
For a lattice of Voronoi's first kind:
\begin{itemize}
\item $x_0$ can be chosen to ensure that a closest lattice point in found after at most $K \leq n$ iterations.
\item Minimisation over the set of relevant vector can be performed by computing a minimimum cut in a flow network.
\item Using known algorithms a minimum cut can be found in $O(n^3)$ operations.
\item In total $O(n^4)$ operations are required to compute a closest lattice point.
\end{itemize}
}

\begin{theorem}
Let $\Lambda$ be a $n$-dimensional lattice of Voronoi's first kind with obtuse superbase $b_1, \dots, b_{n+1}$.  Let $z_1,\dots,z_{n+1} \in \reals$ minimise
\[
\| y - \sum_{n=1}^{n+1} b_i z_i \| 
\]
and put
\[
x_0 = \sum_{n=1}^{n+1} b_i \floor{z_i}.
\]
The iterative proceedure, initialized at $x_0$, converges to a closest lattice point in at most $K \leq n$ iterations.
\end{theorem}
}

@@

\begin{itemize}
\item Can good codes or quantisers be constructed from lattices of Voronoi's first kind?
\item Do applications such as global position, phase unwrapping, circular statistics, etc., involve lattices of Voronoi's first kind?
\end{itemize}

>>>>

\title{Finding shortest and closest vectors in a lattice of Voronoi's first kind}
\author{Robby McKilliam \\
%\vspace{0.2cm}
Alex Grant \\ Vaughan Clarkson \\
\vspace{0.7cm}
{\small
Institute for Telecommunications Research \\ University of South Australia 
\\ \vspace{0.2cm}
School of Information Technology and Electrical Engineering \\ The University of Queensland
}
}

@@

\frame{
\frametitle{A series of relevant vectors}
For a lattice of Voronoi's first kind:
\begin{itemize}
\item $x_0$ can be chosen to ensure that a closest lattice point in found after at most $K \leq n$ iterations.
\item Minimisation over the set of relevant vectors can be performed by computing a minimum cut in a flow network.
\item Using known algorithms a minimum cut can be found in $O(n^3)$ operations.
\item In total $O(n^4)$ operations are required to compute a closest lattice point.
\end{itemize}
}

\frame{
%\frametitle{A series of relevant vectors}

\begin{theorem}
Let $\Lambda$ be a $n$-dimensional lattice of Voronoi's first kind with obtuse superbase $b_1, \dots, b_{n+1}$.  Let $z_1,\dots,z_{n+1} \in \reals$ minimise
\[
\| y - \sum_{n=1}^{n+1} b_i z_i \| 
\]
and put
\[
x_0 = \sum_{n=1}^{n+1} b_i \floor{z_i}.
\]
The iterative procedure, initialized at $x_0$, converges to a closest lattice point in at most $K \leq n$ iterations.
\end{theorem}
}

@@

\begin{itemize}
\item Can good codes or quantisers be constructed from lattices of Voronoi's first kind?
\item Do applications such as global position, phase unwrapping, circular statistics, etc., involve lattices of Voronoi's first kind?
\item Are there subfamilies of Voronoi's first kind that admit even faster algorithms?
\item Are there other families of lattices for which similar techniques lead to polynomial time algorithms?
\end{itemize}
